Random Forests for Automatic Matching Bullet-Lands

### 2015-12-20 imaging-paper.Rnw
cash issues

<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
opts_chunk$set(fig.path='Figure/fig-', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, fig.show='hold', par=TRUE, cache=F, tidy=T, concordance=TRUE, autodep=TRUE, root.dir="../", comment="|", dev="CairoPDF")
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

@@

includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist"))
cc <- read.csv("csvs/crosscuts-25-new.csv")
cc$bullet <- gsub(".*//","",cc$path)
cc$bullet <- gsub(".x3p", "", cc$bullet)
bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
                  bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

excludesObs <- which(bstats$flagged)

rp1 <- rpart(match~., bstats[-excludesObs,includesVar])  # doesn't include cms at all !!!!

@@

<<rforest, echo=FALSE, message=FALSE>>=
library(randomForest)
library(reshape2)
set.seed(20151215)
rtrees <- randomForest(factor(match)~., data=bstats[-excludesObs,includesVar], ntree=300)

>>>>

<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(extrafont)
library(knitr)
imgdir <- "Figure/"
codedir <- "code"
datadir <- "app/images/Hamby252_3DX3P1of2/"

@@

includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist"))
cc <- read.csv("csvs/crosscuts-25-new.csv")
# cc$bullet <- gsub(".*//","",cc$path)
# cc$bullet <- gsub(".x3p", "", cc$bullet)
# bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
#                   bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

#excludesObs <- which(bstats$flagged)

rp1 <- rpart(match~., subset(bstats, !flagged)[,includesVar])  # doesn't include cms at all !!!!

@@

<<rforest, echo=FALSE, message=FALSE>>=
library(randomForest)
library(reshape2)
set.seed(20151215)
rtrees <- randomForest(factor(match)~., data=subset(bstats, !flagged)[,includesVar], ntree=300)
